Hypertension and microbiome

### 2019-01-25 articletwo.Rmd
Minor

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(rvg)
library(tableone)
library(scales)
library(gridExtra)
library(png)
```

@@

```{r EdgeR functions, code=readLines("aaro/edgeR_plot_functions.R")}
source("articletwo-ggplot.R")
```

@@

adonis.species  <- readRDS("rds/adonis.species.rds")

adonis.species$min

@@

```{r save grob}
alpha.diversity <- plot.alpha(diversity)
beta.diversity <- plot.beta(diversity)
gs4 <- list(alpha.diversity$yaxis,
            alpha.diversity$plot,
            beta.diversity$plot,  
            alpha.diversity$legend,
            alpha.diversity$xaxis,
            beta.diversity$xaxis,
           plot.xlab.beta.diversity)

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(1,    2,    3, NA, 4),
                      c(1,    2,    3, NA, NA),
                      c(NA, 5,    6, NA, NA),
                      c(NA, NA, 7, NA, NA)),
                  widths=c(4, 0.7, 5, 0.7, 4),
            heights=c(3, 7, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)

>>>>

```{r libraries, cache = FALSE}
library(dplyr)
library(tibble)
library(phyloseq)
library(microbiome)
library(finriskmetagcommon)
library(knitr)
library(tidyr)
library(vegan)
library(reshape)
library(ggpmisc)
library(Maaslin)
library(parallel)
library(officer)
library(flextable)
library(rvg)
library(tableone)
library(scales)
library(ggplot2)
library(gridExtra)
library(png)
```

@@

```{r EdgeR functions, code=readLines("articletwo-ggplot.R")}
source("articletwo-ggplot.R")
```

@@

adonis.species  <- readRDS("rds/adonis.species.rds")
adonis.species$min

@@

```{r save grob}
alpha.diversity <- plot.alpha(diversity)
beta.diversity <- plot.beta(diversity)
gs4 <- list(alpha.diversity$yaxis,
            alpha.diversity$plot,
            beta.diversity$plot,  
            alpha.diversity$legend,
            alpha.diversity$xaxis,
            beta.diversity$xaxis,
            plot.xlab.beta.diversity,
            text_grob("A", vjust = "top", hjust= "left", size = 20))

g4 <- arrangeGrob(grobs = gs4,
                  layout_matrix = rbind(
                      c(8,    NA,    NA,    NA, NA, 4),
                      c(NA, 1,    2,    3, NA, 4),
                      c(NA, 1,    2,    3, NA, NA),
                      c(NA, NA, 5,    6, NA, NA),
                      c(NA, NA, NA, 7, NA, NA)),
                  widths=c(0.7, 4, 0.7, 5, 0.7, 4),
                  heights=c(1, 1, 6, 1, 2))
ggsave(file = "cache/alpha-beta.png", plot=g4, height=3, width=9)
